HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-20 LaTeX/ms.tex
Use bbl directly in manuscript.

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens

@@

J.~Scudders\altaffilmark{3},

@@

\bibliographystyle{apj}

\bibliography{rbussman}

>>>>

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudder hayward cowley almalens

@@

J.~Scudder\altaffilmark{3},

@@

%\bibliographystyle{apj}

%\bibliography{rbussman}
\begin{thebibliography}{106}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Aravena} {et~al.}(2010){Aravena}, {Bertoldi}, {Carilli},
  {Schinnerer}, {McCracken}, {Salvato}, {Riechers}, {Sheth}, {Sm{\v
  o}lci{\'c}}, {Capak}, {Koekemoer}, \& {Menten}}]{Aravena:2010fr}
{Aravena}, M., {Bertoldi}, F., {Carilli}, C., {Schinnerer}, E., {McCracken},
  H.~J., {Salvato}, M., {Riechers}, D., {Sheth}, K., {Sm{\v o}lci{\'c}}, V.,
  {Capak}, P., {Koekemoer}, A.~M., \& {Menten}, K.~M. 2010, \apjl, 708, L36

\bibitem[{{Barger} {et~al.}(2012){Barger}, {Wang}, {Cowie}, {Owen}, {Chen}, \&
  {Williams}}]{Barger:2012yg}
{Barger}, A.~J., {Wang}, W.-H., {Cowie}, L.~L., {Owen}, F.~N., {Chen}, C.-C.,
  \& {Williams}, J.~P. 2012, \apj, 761, 89

\bibitem[{{Behroozi} {et~al.}(2013{\natexlab{a}}){Behroozi}, {Wechsler}, \&
  {Conroy}}]{Behroozi13c}
{Behroozi}, P.~S., {Wechsler}, R.~H., \& {Conroy}, C. 2013{\natexlab{a}}, \apj,
  770, 57

\bibitem[{{Behroozi} {et~al.}(2013{\natexlab{b}}){Behroozi}, {Wechsler}, \&
  {Wu}}]{Behroozi13a}
{Behroozi}, P.~S., {Wechsler}, R.~H., \& {Wu}, H.-Y. 2013{\natexlab{b}}, \apj,
  762, 109

\bibitem[{{Behroozi} {et~al.}(2013{\natexlab{c}}){Behroozi}, {Wechsler}, {Wu},
  {Busha}, {Klypin}, \& {Primack}}]{Behroozi13b}
{Behroozi}, P.~S., {Wechsler}, R.~H., {Wu}, H.-Y., {Busha}, M.~T., {Klypin},
  A.~A., \& {Primack}, J.~R. 2013{\natexlab{c}}, \apj, 763, 18

\bibitem[{{Blain}(1996)}]{1996MNRAS.283.1340B}
{Blain}, A.~W. 1996, \mnras, 283, 1340

\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell:2013lr}
{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {Genzel}, R., {Ivison},
  R.~J., {Tacconi}, L.~J., {Alaghband-Zadeh}, S., {Bertoldi}, F., {Blain},
  A.~W., {Casey}, C.~M., {Cox}, P., {Greve}, T.~R., {Lutz}, D., {Neri}, R.,
  {Omont}, A., \& {Swinbank}, A.~M. 2013, \mnras, 429, 3047

\bibitem[{{Bussmann} {et~al.}(2012){Bussmann}, {Gurwell}, {Fu}, {Smith}, {Dye},
  {Auld}, {Baes}, {Baker}, {Bonfield}, {Cava}, {Clements}, {Cooray}, {Coppin},
  {Dannerbauer}, {Dariush}, {De Zotti}, {Dunne}, {Eales}, {Fritz}, {Hopwood},
  {Ibar}, {Ivison}, {Jarvis}, {Kim}, {Leeuw}, {Maddox}, {Micha{\l}owski},
  {Negrello}, {Pascale}, {Pohlen}, {Riechers}, {Rigby}, {Scott}, {Temi}, {Van
  der Werf}, {Wardlow}, {Wilner}, \& {Verma}}]{Bussmann:2012lr}
{Bussmann}, R.~S., {Gurwell}, M.~A., {Fu}, H., {Smith}, D.~J.~B., {Dye}, S.,
  {Auld}, R., {Baes}, M., {Baker}, A.~J., {Bonfield}, D., {Cava}, A.,
  {Clements}, D.~L., {Cooray}, A., {Coppin}, K., {Dannerbauer}, H., {Dariush},
  A., {De Zotti}, G., {Dunne}, L., {Eales}, S., {Fritz}, J., {Hopwood}, R.,
  {Ibar}, E., {Ivison}, R.~J., {Jarvis}, M.~J., {Kim}, S., {Leeuw}, L.~L.,
  {Maddox}, S., {Micha{\l}owski}, M.~J., {Negrello}, M., {Pascale}, E.,
  {Pohlen}, M., {Riechers}, D.~A., {Rigby}, E., {Scott}, D., {Temi}, P., {Van
  der Werf}, P.~P., {Wardlow}, J., {Wilner}, D., \& {Verma}, A. 2012, \apj, 756

\bibitem[{{Bussmann} {et~al.}(2013){Bussmann}, {P{\'e}rez-Fournon}, {Amber},
  {Calanog}, {Gurwell}, {Dannerbauer}, {De Bernardis}, {Fu}, {Harris}, {Krips},
  {Lapi}, {Maiolino}, {Omont}, {Riechers}, {Wardlow}, {Baker}, {Birkinshaw},
  {Bock}, {Bourne}, {Clements}, {Cooray}, {De Zotti}, {Dunne}, {Dye}, {Eales},
  {Farrah}, {Gavazzi}, {Gonz{\'a}lez Nuevo}, {Hopwood}, {Ibar}, {Ivison},
  {Laporte}, {Maddox}, {Mart{\'{\i}}nez-Navajas}, {Michalowski}, {Negrello},
  {Oliver}, {Roseboom}, {Scott}, {Serjeant}, {Smith}, {Smith}, {Streblyanska},
  {Valiante}, {van der Werf}, {Verma}, {Vieira}, {Wang}, \&
  {Wilner}}]{Bussmann:2013lr}
{Bussmann}, R.~S., {P{\'e}rez-Fournon}, I., {Amber}, S., {Calanog}, J.,
  {Gurwell}, M.~A., {Dannerbauer}, H., {De Bernardis}, F., {Fu}, H., {Harris},
  A.~I., {Krips}, M., {Lapi}, A., {Maiolino}, R., {Omont}, A., {Riechers}, D.,
  {Wardlow}, J., {Baker}, A.~J., {Birkinshaw}, M., {Bock}, J., {Bourne}, N.,
  {Clements}, D.~L., {Cooray}, A., {De Zotti}, G., {Dunne}, L., {Dye}, S.,
  {Eales}, S., {Farrah}, D., {Gavazzi}, R., {Gonz{\'a}lez Nuevo}, J.,
  {Hopwood}, R., {Ibar}, E., {Ivison}, R.~J., {Laporte}, N., {Maddox}, S.,
  {Mart{\'{\i}}nez-Navajas}, P., {Michalowski}, M., {Negrello}, M., {Oliver},
  S.~J., {Roseboom}, I.~G., {Scott}, D., {Serjeant}, S., {Smith}, A.~J.,
  {Smith}, M., {Streblyanska}, A., {Valiante}, E., {van der Werf}, P., {Verma},
  A., {Vieira}, J.~D., {Wang}, L., \& {Wilner}, D. 2013, \apj, 779, 25

\bibitem[{{Calanog} {et~al.}(2014){Calanog}, {Fu}, {Cooray}, {Wardlow}, {Ma},
  {Amber}, {Baes}, {Bock}, {Bourne}, {Bussmann}, {Casey}, {Chapman},
  {Clements}, {Conley}, {Dannerbauer}, {DeZotti}, {Dunne}, {Dye}, {Eales},
  {Farrah}, {Furlanetto}, {Harris}, {Ivison}, {Maddox}, {Magdis},
  {Michalowski}, {Negrello}, {Nightingale}, {O'Bryan}, {Oliver}, {Riechers},
  {Scott}, {Serjeant}, {Simpson}, {Smith}, {Timmons}, {Thacker}, {Valiante}, \&
  {Vieira}}]{Calanog:2014lr}
{Calanog}, J.~A., {Fu}, H., {Cooray}, A., {Wardlow}, J., {Ma}, B., {Amber}, S.,
  {Baes}, M., {Bock}, J., {Bourne}, N., {Bussmann}, R.~S., {Casey}, C.~M.,
  {Chapman}, S.~C., {Clements}, D.~L., {Conley}, A., {Dannerbauer}, H.,
  {DeZotti}, G., {Dunne}, L., {Dye}, S., {Eales}, S., {Farrah}, D.,
  {Furlanetto}, C., {Harris}, A.~I., {Ivison}, R.~J., {Maddox}, S.~J.,
  {Magdis}, G., {Michalowski}, M.~J., {Negrello}, M., {Nightingale}, J.,
  {O'Bryan}, J.~M., {Oliver}, S.~J., {Riechers}, D., {Scott}, D., {Serjeant},
  S., {Simpson}, J., {Smith}, M., {Timmons}, N., {Thacker}, C., {Valiante}, E.,
  \& {Vieira}, J.~D. 2014, ArXiv e-prints

\bibitem[{{Capak} {et~al.}(2011){Capak}, {Riechers}, {Scoville}, {Carilli},
  {Cox}, {Neri}, {Robertson}, {Salvato}, {Schinnerer}, {Yan}, {Wilson}, {Yun},
  {Civano}, {Elvis}, {Karim}, {Mobasher}, \& {Staguhn}}]{Capak:2011qy}
{Capak}, P.~L., {Riechers}, D., {Scoville}, N.~Z., {Carilli}, C., {Cox}, P.,
  {Neri}, R., {Robertson}, B., {Salvato}, M., {Schinnerer}, E., {Yan}, L.,
  {Wilson}, G.~W., {Yun}, M., {Civano}, F., {Elvis}, M., {Karim}, A.,
  {Mobasher}, B., \& {Staguhn}, J.~G. 2011, \nat, 470, 233

\bibitem[{{Carlstrom} {et~al.}(2011)}]{Carlstrom:2011qy}
{Carlstrom}, J.~E. {et~al.} 2011, \pasp, 123, 568

\bibitem[{{Casey} {et~al.}(2012{\natexlab{a}}){Casey}, {Berta},
  {B{\'e}thermin}, {Bock}, {Bridge}, {Budynkiewicz}, {Burgarella}, {Chapin},
  {Chapman}, {Clements}, {Conley}, {Conselice}, {Cooray}, {Farrah},
  {Hatziminaoglou}, {Ivison}, {le Floc'h}, {Lutz}, {Magdis}, {Magnelli},
  {Oliver}, {Page}, {Pozzi}, {Rigopoulou}, {Riguccini}, {Roseboom}, {Sanders},
  {Scott}, {Seymour}, {Valtchanov}, {Vieira}, {Viero}, \&
  {Wardlow}}]{Casey:2012qy}
{Casey}, C.~M., {Berta}, S., {B{\'e}thermin}, M., {Bock}, J., {Bridge}, C.,
  {Budynkiewicz}, J., {Burgarella}, D., {Chapin}, E., {Chapman}, S.~C.,
  {Clements}, D.~L., {Conley}, A., {Conselice}, C.~J., {Cooray}, A., {Farrah},
  D., {Hatziminaoglou}, E., {Ivison}, R.~J., {le Floc'h}, E., {Lutz}, D.,
  {Magdis}, G., {Magnelli}, B., {Oliver}, S.~J., {Page}, M.~J., {Pozzi}, F.,
  {Rigopoulou}, D., {Riguccini}, L., {Roseboom}, I.~G., {Sanders}, D.~B.,
  {Scott}, D., {Seymour}, N., {Valtchanov}, I., {Vieira}, J.~D., {Viero}, M.,
  \& {Wardlow}, J. 2012{\natexlab{a}}, \apj, 761, 140

\bibitem[{{Casey} {et~al.}(2012{\natexlab{b}}){Casey}, {Berta},
  {B{\'e}thermin}, {Bock}, {Bridge}, {Burgarella}, {Chapin}, {Chapman},
  {Clements}, {Conley}, {Conselice}, {Cooray}, {Farrah}, {Hatziminaoglou},
  {Ivison}, {le Floc'h}, {Lutz}, {Magdis}, {Magnelli}, {Oliver}, {Page},
  {Pozzi}, {Rigopoulou}, {Riguccini}, {Roseboom}, {Sanders}, {Scott},
  {Seymour}, {Valtchanov}, {Vieira}, {Viero}, \& {Wardlow}}]{Casey:2012uq}
{Casey}, C.~M., {Berta}, S., {B{\'e}thermin}, M., {Bock}, J., {Bridge}, C.,
  {Burgarella}, D., {Chapin}, E., {Chapman}, S.~C., {Clements}, D.~L.,
  {Conley}, A., {Conselice}, C.~J., {Cooray}, A., {Farrah}, D.,
  {Hatziminaoglou}, E., {Ivison}, R.~J., {le Floc'h}, E., {Lutz}, D., {Magdis},
  G., {Magnelli}, B., {Oliver}, S.~J., {Page}, M.~J., {Pozzi}, F.,
  {Rigopoulou}, D., {Riguccini}, L., {Roseboom}, I.~G., {Sanders}, D.~B.,
  {Scott}, D., {Seymour}, N., {Valtchanov}, I., {Vieira}, J.~D., {Viero}, M.,
  \& {Wardlow}, J. 2012{\natexlab{b}}, \apj, 761, 139

\bibitem[{{Casey} {et~al.}(2014){Casey}, {Narayanan}, \&
  {Cooray}}]{Casey:2014lr}
{Casey}, C.~M., {Narayanan}, D., \& {Cooray}, A. 2014, \physrep, 541, 45

\bibitem[{{Chapman} {et~al.}(2005){Chapman}, {Blain}, {Smail}, \&
  {Ivison}}]{2005ApJ...622..772C}
{Chapman}, S.~C., {Blain}, A.~W., {Smail}, I., \& {Ivison}, R.~J. 2005, \apj,
  622, 772

\bibitem[{{Cole} {et~al.}(2000){Cole}, {Lacey}, {Baugh}, \&
  {Frenk}}]{Cole:2000fk}
{Cole}, S., {Lacey}, C.~G., {Baugh}, C.~M., \& {Frenk}, C.~S. 2000, \mnras,
  319, 168

\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
  {Perley}, {Taylor}, \& {Broderick}}]{Condon:1998uq}
{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {Yin}, Q.~F., {Perley},
  R.~A., {Taylor}, G.~B., \& {Broderick}, J.~J. 1998, \aj, 115, 1693

\bibitem[{{Conley} {et~al.}(2011)}]{Conley:2011lr}
{Conley}, A. {et~al.} 2011, \apjl, 732, L35

\bibitem[{{Cooray} {et~al.}(2014){Cooray}, {Calanog}, {Wardlow}, {Bock},
  {Bridge}, {Burgarella}, {Bussmann}, {Casey}, {Clements}, {Conley}, {Farrah},
  {Fu}, {Gavazzi}, {Ivison}, {La Porte}, {Lo Faro}, {Ma}, {Magdis}, {Oliver},
  {Osage}, {P{\'e}rez-Fournon}, {Riechers}, {Rigopoulou}, {Scott}, {Viero}, \&
  {Watson}}]{Cooray:2014rm}
{Cooray}, A., {Calanog}, J., {Wardlow}, J.~L., {Bock}, J., {Bridge}, C.,
  {Burgarella}, D., {Bussmann}, R.~S., {Casey}, C.~M., {Clements}, D.,
  {Conley}, A., {Farrah}, D., {Fu}, H., {Gavazzi}, R., {Ivison}, R.~J., {La
  Porte}, N., {Lo Faro}, B., {Ma}, B., {Magdis}, G., {Oliver}, S.~J., {Osage},
  W.~A., {P{\'e}rez-Fournon}, I., {Riechers}, D., {Rigopoulou}, D., {Scott},
  D., {Viero}, M., \& {Watson}, D. 2014, \apj, 790, 40

\bibitem[{{Cowley} {et~al.}(2015){Cowley}, {Lacey}, {Baugh}, \&
  {Cole}}]{Cowley:2015lr}
{Cowley}, W.~I., {Lacey}, C.~G., {Baugh}, C.~M., \& {Cole}, S. 2015, \mnras,
  446, 1784

\bibitem[{{Cox} {et~al.}(2008){Cox}, {Jonsson}, {Somerville}, {Primack}, \&
  {Dekel}}]{Cox08}
{Cox}, T.~J., {Jonsson}, P., {Somerville}, R.~S., {Primack}, J.~R., \& {Dekel},
  A. 2008, \mnras, 384, 386

\bibitem[{{Daddi} {et~al.}(2009)}]{Daddi:2009qy}
{Daddi}, E. {et~al.} 2009, \apj, 694, 1517

\bibitem[{{Dye} {et~al.}(2015){Dye}, {Furlanetto}, {Swinbank}, {Vlahakis},
  {Nightingale}, {Dunne}, {Eales}, {Smail}, {Oteo-Gomez}, {Hunter}, {Negrello},
  {Dannerbauer}, {Ivison}, {Gavazzi}, {Cooray}, \& {van der Werf}}]{Dye:2015fp}
{Dye}, S., {Furlanetto}, C., {Swinbank}, A.~M., {Vlahakis}, C., {Nightingale},
  J.~W., {Dunne}, L., {Eales}, S.~A., {Smail}, I., {Oteo-Gomez}, I., {Hunter},
  T., {Negrello}, M., {Dannerbauer}, H., {Ivison}, R.~J., {Gavazzi}, R.,
  {Cooray}, A., \& {van der Werf}, P. 2015, ArXiv e-prints

\bibitem[{{Eales} {et~al.}(2010)}]{2010PASP..122..499E}
{Eales}, S. {et~al.} 2010, \pasp, 122, 499

\bibitem[{{Engel} {et~al.}(2010){Engel}, {Tacconi}, {Davies}, {Neri}, {Smail},
  {Chapman}, {Genzel}, {Cox}, {Greve}, {Ivison}, {Blain}, {Bertoldi}, \&
  {Omont}}]{2010ApJ...724..233E}
{Engel}, H., {Tacconi}, L.~J., {Davies}, R.~I., {Neri}, R., {Smail}, I.,
  {Chapman}, S.~C., {Genzel}, R., {Cox}, P., {Greve}, T.~R., {Ivison}, R.~J.,
  {Blain}, A., {Bertoldi}, F., \& {Omont}, A. 2010, \apj, 724, 233

\bibitem[{{Fialkov} \& {Loeb}(2015)}]{Fialkov:2015eu}
{Fialkov}, A. \& {Loeb}, A. 2015, ArXiv e-prints

\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
  {Goodman}}]{Foreman-Mackey:2013yq}
{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
  125, 306

\bibitem[{{Fu} {et~al.}(2013)}]{Fu:2013lr}
{Fu}, H. {et~al.} 2013, \nat, 498, 338

\bibitem[{{Gavazzi} {et~al.}(2011)}]{Gavazzi:2011lr}
{Gavazzi}, R. {et~al.} 2011, \apj, 738, 125

\bibitem[{{Goodman} \& {Weare}(2010)}]{goodmanweare}
{Goodman}, J. \& {Weare}, J. 2010, Communications in Applied Mathematics and
  Computational Science, 5, 65

\bibitem[{{Griffin} {et~al.}(2010)}]{2010A&A...518L...3G}
{Griffin}, M.~J. {et~al.} 2010, \aap, 518, L3+

\bibitem[{{Guo} {et~al.}(2013){Guo}, {White}, {Angulo}, {Henriques}, {Lemson},
  {Boylan-Kolchin}, {Thomas}, \& {Short}}]{Guo:2013lr}
{Guo}, Q., {White}, S., {Angulo}, R.~E., {Henriques}, B., {Lemson}, G.,
  {Boylan-Kolchin}, M., {Thomas}, P., \& {Short}, C. 2013, \mnras, 428, 1351

\bibitem[{{Hayward} {et~al.}(2013{\natexlab{a}}){Hayward}, {Behroozi},
  {Somerville}, {Primack}, {Moreno}, \& {Wechsler}}]{HB13}
{Hayward}, C.~C., {Behroozi}, P.~S., {Somerville}, R.~S., {Primack}, J.~R.,
  {Moreno}, J., \& {Wechsler}, R.~H. 2013{\natexlab{a}}, \mnras

\bibitem[{{Hayward} {et~al.}(2012{\natexlab{a}}){Hayward}, {Jonsson}, {Kere{\v
  s}}, {Magnelli}, {Hernquist}, \& {Cox}}]{Hayward:2012lr}
{Hayward}, C.~C., {Jonsson}, P., {Kere{\v s}}, D., {Magnelli}, B., {Hernquist},
  L., \& {Cox}, T.~J. 2012{\natexlab{a}}, \mnras, 424, 951

\bibitem[{{Hayward} {et~al.}(2012{\natexlab{b}}){Hayward}, {Jonsson}, {Kere{\v
  s}}, {Magnelli}, {Hernquist}, \& {Cox}}]{H12}
---. 2012{\natexlab{b}}, \mnras, 424, 951

\bibitem[{{Hayward} {et~al.}(2011){Hayward}, {Kere{\v s}}, {Jonsson},
  {Narayanan}, {Cox}, \& {Hernquist}}]{H11}
{Hayward}, C.~C., {Kere{\v s}}, D., {Jonsson}, P., {Narayanan}, D., {Cox},
  T.~J., \& {Hernquist}, L. 2011, \apj, 743, 159

\bibitem[{{Hayward} {et~al.}(2013{\natexlab{b}}){Hayward}, {Narayanan},
  {Kere{\v s}}, {Jonsson}, {Hopkins}, {Cox}, \& {Hernquist}}]{HN13}
{Hayward}, C.~C., {Narayanan}, D., {Kere{\v s}}, D., {Jonsson}, P., {Hopkins},
  P.~F., {Cox}, T.~J., \& {Hernquist}, L. 2013{\natexlab{b}}, \mnras, 428, 2529

\bibitem[{{Hayward} {et~al.}(2014){Hayward}, {Torrey}, {Springel}, {Hernquist},
  \& {Vogelsberger}}]{H14}
{Hayward}, C.~C., {Torrey}, P., {Springel}, V., {Hernquist}, L., \&
  {Vogelsberger}, M. 2014, \mnras, 442, 1992

\bibitem[{{Hezaveh} {et~al.}(2013)}]{Hezaveh:2013fk}
{Hezaveh}, Y.~D. {et~al.} 2013, \apj, 767, 132

\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
  \& {Wright}}]{Hinshaw:2013ty}
{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
  {Wright}, E.~L. 2013, \apjs, 208, 19

\bibitem[{{Ho} {et~al.}(2004){Ho}, {Moran}, \& {Lo}}]{Ho:2004lr}
{Ho}, P.~T.~P., {Moran}, J.~M., \& {Lo}, K.~Y. 2004, \apjl, 616, L1

\bibitem[{{Hodge} {et~al.}(2013)}]{Hodge:2013qy}
{Hodge}, J.~A. {et~al.} 2013, \apj, 768, 91

\bibitem[{{Hook} {et~al.}(2004){Hook}, {J{\o}rgensen}, {Allington-Smith},
  {Davies}, {Metcalfe}, {Murowinski}, \& {Crampton}}]{Hook:2004qy}
{Hook}, I.~M., {J{\o}rgensen}, I., {Allington-Smith}, J.~R., {Davies}, R.~L.,
  {Metcalfe}, N., {Murowinski}, R.~G., \& {Crampton}, D. 2004, \pasp, 116, 425

\bibitem[{{Ikarashi} {et~al.}(2014){Ikarashi}, {Ivison}, {Caputi}, {Aretxaga},
  {Dunlop}, {Hatsukade}, {Hughes}, {Iono}, {Izumi}, {Kawabe}, {Kohno}, {Lagos},
  {Motohara}, {Nakanishi}, {Ohta}, {Tamura}, {Umehata}, {Wilson}, {Yabe}, \&
  {Yun}}]{Ikarashi:2014nr}
{Ikarashi}, S., {Ivison}, R.~J., {Caputi}, K.~I., {Aretxaga}, I., {Dunlop},
  J.~S., {Hatsukade}, B., {Hughes}, D., {Iono}, D., {Izumi}, T., {Kawabe}, R.,
  {Kohno}, K., {Lagos}, C.~P., {Motohara}, K., {Nakanishi}, K., {Ohta}, K.,
  {Tamura}, Y., {Umehata}, H., {Wilson}, G., {Yabe}, K., \& {Yun}, M.~S. 2014,
  ArXiv e-prints

\bibitem[{{Ikarashi} {et~al.}(2011)}]{Ikarashi:2011qy}
{Ikarashi}, S. {et~al.} 2011, \mnras, 415, 3081

\bibitem[{{Ivison} {et~al.}(2007){Ivison}, {Greve}, {Dunlop}, {Peacock},
  {Egami}, {Smail}, {Ibar}, {van Kampen}, {Aretxaga}, {Babbedge}, {Biggs},
  {Blain}, {Chapman}, {Clements}, {Coppin}, {Farrah}, {Halpern}, {Hughes},
  {Jarvis}, {Jenness}, {Jones}, {Mortier}, {Oliver}, {Papovich},
  {P{\'e}rez-Gonz{\'a}lez}, {Pope}, {Rawlings}, {Rieke}, {Rowan-Robinson},
  {Savage}, {Scott}, {Seigar}, {Serjeant}, {Simpson}, {Stevens}, {Vaccari},
  {Wagg}, \& {Willott}}]{Ivison:2007qv}
{Ivison}, R.~J., {Greve}, T.~R., {Dunlop}, J.~S., {Peacock}, J.~A., {Egami},
  E., {Smail}, I., {Ibar}, E., {van Kampen}, E., {Aretxaga}, I., {Babbedge},
  T., {Biggs}, A.~D., {Blain}, A.~W., {Chapman}, S.~C., {Clements}, D.~L.,
  {Coppin}, K., {Farrah}, D., {Halpern}, M., {Hughes}, D.~H., {Jarvis}, M.~J.,
  {Jenness}, T., {Jones}, J.~R., {Mortier}, A.~M.~J., {Oliver}, S., {Papovich},
  C., {P{\'e}rez-Gonz{\'a}lez}, P.~G., {Pope}, A., {Rawlings}, S., {Rieke},
  G.~H., {Rowan-Robinson}, M., {Savage}, R.~S., {Scott}, D., {Seigar}, M.,
  {Serjeant}, S., {Simpson}, C., {Stevens}, J.~A., {Vaccari}, M., {Wagg}, J.,
  \& {Willott}, C.~J. 2007, \mnras, 380, 199

\bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
  {Thomson}, {Xilouris}, \& {Chapman}}]{2011MNRAS.412.1913I}
{Ivison}, R.~J., {Papadopoulos}, P.~P., {Smail}, I., {Greve}, T.~R., {Thomson},
  A.~P., {Xilouris}, E.~M., \& {Chapman}, S.~C. 2011, \mnras, 412, 1913

\bibitem[{{Ivison} {et~al.}(2013)}]{Ivison:2013fk}
{Ivison}, R.~J. {et~al.} 2013, \apj, 772, 137

\bibitem[{{Jiang} {et~al.}(2014){Jiang}, {Helly}, {Cole}, \&
  {Frenk}}]{Jiang:2014lr}
{Jiang}, L., {Helly}, J.~C., {Cole}, S., \& {Frenk}, C.~S. 2014, \mnras, 440,
  2115

\bibitem[{{Karim} {et~al.}(2013)}]{Karim:2013lr}
{Karim}, A. {et~al.} 2013, \mnras, 432, 2

\bibitem[{{Keeton}(2001)}]{Keeton:2001lr}
{Keeton}, C.~R. 2001, ArXiv Astrophysics e-prints

\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
  {Primack}}]{Klypin11}
{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102

\bibitem[{{Kochanek}(1994)}]{Kochanek:1994fk}
{Kochanek}, C.~S. 1994, \apj, 436, 56

\bibitem[{{Komatsu} {et~al.}(2011){Komatsu}, {Smith}, {Dunkley}, {Bennett},
  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Nolta}, {Page}, {Spergel},
  {Halpern}, {Hill}, {Kogut}, {Limon}, {Meyer}, {Odegard}, {Tucker}, {Weiland},
  {Wollack}, \& {Wright}}]{Komatsu:2011fk}
{Komatsu}, E., {Smith}, K.~M., {Dunkley}, J., {Bennett}, C.~L., {Gold}, B.,
  {Hinshaw}, G., {Jarosik}, N., {Larson}, D., {Nolta}, M.~R., {Page}, L.,
  {Spergel}, D.~N., {Halpern}, M., {Hill}, R.~S., {Kogut}, A., {Limon}, M.,
  {Meyer}, S.~S., {Odegard}, N., {Tucker}, G.~S., {Weiland}, J.~L., {Wollack},
  E., \& {Wright}, E.~L. 2011, \apjs, 192, 18

\bibitem[{{Lilly} {et~al.}(1996){Lilly}, {Le Fevre}, {Hammer}, \&
  {Crampton}}]{Lilly:1996uq}
{Lilly}, S.~J., {Le Fevre}, O., {Hammer}, F., \& {Crampton}, D. 1996, \apjl,
  460, L1

\bibitem[{{Lima} {et~al.}(2010){Lima}, {Jain}, \& {Devlin}}]{Lima:2010fk}
{Lima}, M., {Jain}, B., \& {Devlin}, M. 2010, \mnras, 406, 2352

\bibitem[{{Madau} {et~al.}(1996){Madau}, {Ferguson}, {Dickinson}, {Giavalisco},
  {Steidel}, \& {Fruchter}}]{1996MNRAS.283.1388M}
{Madau}, P., {Ferguson}, H.~C., {Dickinson}, M.~E., {Giavalisco}, M.,
  {Steidel}, C.~C., \& {Fruchter}, A. 1996, \mnras, 283, 1388

\bibitem[{{Magnelli} {et~al.}(2011){Magnelli}, {Elbaz}, {Chary}, {Dickinson},
  {Le Borgne}, {Frayer}, \& {Willmer}}]{Magnelli:2011ul}
{Magnelli}, B., {Elbaz}, D., {Chary}, R.~R., {Dickinson}, M., {Le Borgne}, D.,
  {Frayer}, D.~T., \& {Willmer}, C.~N.~A. 2011, \aap, 528, A35+

\bibitem[{{Mandelbaum} {et~al.}(2005){Mandelbaum}, {Tasitsiomi}, {Seljak},
  {Kravtsov}, \& {Wechsler}}]{Mandelbaum:2005lr}
{Mandelbaum}, R., {Tasitsiomi}, A., {Seljak}, U., {Kravtsov}, A.~V., \&
  {Wechsler}, R.~H. 2005, \mnras, 362, 1451

\bibitem[{{Merson} {et~al.}(2013){Merson}, {Baugh}, {Helly}, {Gonzalez-Perez},
  {Cole}, {Bielby}, {Norberg}, {Frenk}, {Benson}, {Bower}, {Lacey}, \&
  {Lagos}}]{Merson:2013lr}
{Merson}, A.~I., {Baugh}, C.~M., {Helly}, J.~C., {Gonzalez-Perez}, V., {Cole},
  S., {Bielby}, R., {Norberg}, P., {Frenk}, C.~S., {Benson}, A.~J., {Bower},
  R.~G., {Lacey}, C.~G., \& {Lagos}, C.~d.~P. 2013, \mnras, 429, 556

\bibitem[{{Messias} {et~al.}(2014){Messias}, {Dye}, {Nagar}, {Orellana},
  {Bussmann}, {Calanog}, {Dannerbauer}, {Fu}, {Ibar}, {Inohara}, {Ivison},
  {Negrello}, {Riechers}, {Sheen}, {Aguirre}, {Amber}, {Birkinshaw}, {Bourne},
  {Bradford}, {Clements}, {Cooray}, {De Zotti}, {Demarco}, {Dunne}, {Eales},
  {Fleuren}, {Kamenetzky}, {Lupu}, {Maddox}, {Marrone}, {Micha{\l}owski},
  {Murphy}, {Nguyen}, {Omont}, {Rowlands}, {Smith}, {Smith}, {Valiante}, \&
  {Vieira}}]{Messias:2014fk}
{Messias}, H., {Dye}, S., {Nagar}, N., {Orellana}, G., {Bussmann}, R.~S.,
  {Calanog}, J., {Dannerbauer}, H., {Fu}, H., {Ibar}, E., {Inohara}, A.,
  {Ivison}, R.~J., {Negrello}, M., {Riechers}, D.~A., {Sheen}, Y.-K.,
  {Aguirre}, J.~E., {Amber}, S., {Birkinshaw}, M., {Bourne}, N., {Bradford},
  C.~M., {Clements}, D.~L., {Cooray}, A., {De Zotti}, G., {Demarco}, R.,
  {Dunne}, L., {Eales}, S., {Fleuren}, S., {Kamenetzky}, J., {Lupu}, R.~E.,
  {Maddox}, S.~J., {Marrone}, D.~P., {Micha{\l}owski}, M.~J., {Murphy}, E.~J.,
  {Nguyen}, H.~T., {Omont}, A., {Rowlands}, K., {Smith}, D., {Smith}, M.,
  {Valiante}, E., \& {Vieira}, J.~D. 2014, \aap, 568, A92
